NTM CT Scoring - Initial Agreement

### 2023-06-28 Stacey Martiniano/ntm_agreement.qmd
fixed section labels
compare scores by individual scorer

---
title: "NTM CT Scoring - Initial Agreement"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
editor: source
---

```{r}
#| include: false
library(tidyverse)
library(irr)
library(redcapAPI)
library(Hmisc)
library(DT)
library(RColorBrewer)
library(knitr)
library(pheatmap)
library(arsenal)
# Import data
api <- read.table("~/Documents/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/api.txt",
                  header = F
)
rcon <- redcapConnection(
  url = "https://redcap.ucdenver.edu/api/",
  token = api[1, 1]
)
data <- exportRecords(rcon, labels = F)
data <- data.frame(lapply(data, as.character))
data$scan_id <- as.numeric(data$scan_id)
# Make scorer IDs by initial
data$scorer <- paste0(
  toupper(substr(data$reader_first_name, 1, 1)),
  toupper(substr(data$reader_last_name, 1, 1))
)
data$scorer[data$scorer == "GG"] <- "GS"
# Deidentify readers
old <- c("AF", "DL", "JW")
new <- c("A", "B", "C")
data$scorer[data$scorer %in% old] <- new[match(data$scorer, old, nomatch = 0)]
# Revert duplicate IDs back to original to match with gold standard
training <- read.csv("~/Documents/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Clean/training.key.csv")
dups <- read.csv("~/Documents/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Clean/duplicated.key.csv")
training$Training_id <- as.numeric(sub("T00", "", training$Training_id))
# Change duplicates to OG IDs
old <- dups$duplicated_ssid..dates.shifted..17.days.
new <- dups$original_ssid
data$scan_id[data$scan_id %in% old] <- new[match(data$scan_id, old, nomatch = 0)]
# Change training IDs to OG IDs
old <- training$Training_id
new <- training$Cffid.Scoring.Set
data$scan_id[data$scan_id %in% old] <- new[match(data$scan_id, old, nomatch = 0)]
# Plot colors
name <- "Accent"
colors <- brewer.pal(6, name)
names(colors) <- c("Checked", "Unchecked", "Absent", "Cylindric", "Varicose", NA)
custom_colors <- scale_fill_manual(name = "", values = colors)
```

@@

```{r}
# Import disease state
outcomes = read.csv("~/Documents/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Clean/disease.key.csv",na.strings = "")
outcomes$NTM.PD..Y.N. = factor(outcomes$NTM.PD..Y.N.,
                               levels = c("No","Yes"),ordered = T)
# Remove training scans, get first reading of duplicates, convert to numeric
scores = data %>% 
  filter(scan_id %in% outcomes$cff_registry_id,scorer != "GS") %>%
  group_by(scorer,scan_id) %>%
  slice_min(scoresheet_timestamp) %>% 
  select(scorer, scan_id, bronchiectasis_rul:atelectasis___6) %>%
  mutate(across(contains("bronchiectasis"),
                ~as.numeric(factor(.x,levels=c("Absent","Cylindric",
                                               "Varicose","Cystic")))-1),
         across(mucoid_impaction___1:atelectasis___6,
                ~as.numeric(factor(.x,levels=c("Unchecked","Checked")))-1))
# Add outcome info
scores = left_join(scores,outcomes %>% select(cff_registry_id,NTM.PD..Y.N.),
                   by = join_by(scan_id == cff_registry_id)) %>%
  rename(`NTM-PD` = NTM.PD..Y.N.)
# Calculate scores
majority = scores %>%
  group_by(scan_id) %>%
  summarise(across(bronchiectasis_rul:`NTM-PD`,
                   ~tail(names(sort(table(.x))), 1)))
max = scores %>%
  group_by(scan_id) %>%
  summarise(across(bronchiectasis_rul:`NTM-PD`,
                   ~max(.x,na.rm = T)))
```

@@

@@

>>>>

---
title: "NTM CT Scoring - Initial Agreement"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
editor: source
execute:
  waring: false
---

```{r}
#| include: false
library(tidyverse)
library(irr)
library(redcapAPI)
library(Hmisc)
library(DT)
library(RColorBrewer)
library(knitr)
library(pheatmap)
library(arsenal)
# Import data
api <- read.table("/Users/timvigers/Library/CloudStorage/Dropbox/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/api.txt",
                  header = F
)
rcon <- redcapConnection(
  url = "https://redcap.ucdenver.edu/api/",
  token = api[1, 1]
)
data <- exportRecords(rcon, labels = F)
data <- data.frame(lapply(data, as.character))
data$scan_id <- as.numeric(data$scan_id)
# Make scorer IDs by initial
data$scorer <- paste0(
  toupper(substr(data$reader_first_name, 1, 1)),
  toupper(substr(data$reader_last_name, 1, 1))
)
data$scorer[data$scorer == "GG"] <- "GS"
# Deidentify readers
old <- c("AF", "DL", "JW")
new <- c("A", "B", "C")
data$scorer[data$scorer %in% old] <- new[match(data$scorer, old, nomatch = 0)]
# Revert duplicate IDs back to original to match with gold standard
training <- read.csv("/Users/timvigers/Library/CloudStorage/Dropbox/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Clean/training.key.csv")
dups <- read.csv("/Users/timvigers/Library/CloudStorage/Dropbox/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Clean/duplicated.key.csv")
training$Training_id <- as.numeric(sub("T00", "", training$Training_id))
# Change duplicates to OG IDs
old <- dups$duplicated_ssid..dates.shifted..17.days.
new <- dups$original_ssid
data$scan_id[data$scan_id %in% old] <- new[match(data$scan_id, old, nomatch = 0)]
# Change training IDs to OG IDs
old <- training$Training_id
new <- training$Cffid.Scoring.Set
data$scan_id[data$scan_id %in% old] <- new[match(data$scan_id, old, nomatch = 0)]
# Plot colors
name <- "Accent"
colors <- brewer.pal(6, name)
names(colors) <- c("Checked", "Unchecked", "Absent", "Cylindric", "Varicose", NA)
custom_colors <- scale_fill_manual(name = "", values = colors)
```

@@

```{r}
# Import disease state
outcomes = read.csv("/Users/timvigers/Library/CloudStorage/Dropbox/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Clean/disease.key.csv",na.strings = "")
outcomes$NTM.PD..Y.N. = factor(outcomes$NTM.PD..Y.N.,
                               levels = c("No","Yes"),ordered = T)
# Remove training scans, get first reading of duplicates, convert to numeric
scores = data %>% 
  filter(scan_id %in% outcomes$cff_registry_id,scorer != "GS") %>%
  group_by(scorer,scan_id) %>%
  slice_min(scoresheet_timestamp) %>% 
  select(scorer, scan_id, bronchiectasis_rul:atelectasis___6) %>%
  mutate(across(contains("bronchiectasis"),
                ~as.numeric(factor(.x,levels=c("Absent","Cylindric",
                                               "Varicose","Cystic")))-1),
         across(mucoid_impaction___1:atelectasis___6,
                ~as.numeric(factor(.x,levels=c("Unchecked","Checked")))-1))
# Add outcome info
scores = left_join(scores,outcomes %>% select(cff_registry_id,NTM.PD..Y.N.),
                   by = join_by(scan_id == cff_registry_id)) %>%
  rename(`NTM-PD` = NTM.PD..Y.N.)
# Calculate scores
majority = scores %>%
  group_by(scan_id) %>%
  summarise(across(bronchiectasis_rul:`NTM-PD`,
                   ~tail(names(sort(table(.x))), 1)))
max = scores %>%
  group_by(scan_id) %>%
  summarise(across(bronchiectasis_rul:`NTM-PD`,
                   ~max(.x,na.rm = T)))
a = scores %>%
  filter(scorer == "A")
b = scores %>%
  filter(scorer == "B") 
c = scores %>%
  filter(scorer == "C")
```

@@

## Using maximum score for each feature

@@

## Scorer A

```{r results='asis'}
comp_score(a)
```

## Scorer B

```{r results='asis'}
comp_score(b)
```

## Scorer C

```{r results='asis'}
comp_score(c)
```
